---
title: How TV Affected Registration in the 2016 Election
author: ''
date: '2020-11-14'
slug: []
categories: []
tags: []
---

This post will be very similar to my last. This post will cover the code and my findings for how the TV shows from the ANES 2016 survey affected registration in 2016. From my last post you will remember that very few shows had an affect on turnout. I predict that since registration is an easier action to preform the shows that had an affect on turnout will just have a more pronounced affect on registration with perhaps a few more shows having a significant affect on registration. What I mean by registration is whether or not the respondent was registered to vote in 2016 just as a clarification. Below is the complete code. The grouping and regression methods were the same for here aswell.

### Libraries ###
```{r}

library(ggplot2)

library(tidyverse)

library(anesr)

library(coefplot)

```


### Data ###

```{r}

data("timeseries_2016")

anes16 <- timeseries_2016 

TV <- anes16 %>% select(V161364, V161365, V161366, V161367, V161368, V161369, V161370, V161371, V161372, V161373, V161374, V161375, V161376, V161377, V161378, V161379, V161380, V161381, V161382, V161383, V161384, V161385, V161386, V161387, V161388, V161389, V161390, V161391, V161392, V161393, V161394, V161395, V161396, V161397, V161398, V161399, V161400, V161401, V161402, V161403, V161404, V161405, V161406, V161407, V161408, V161409, V161410, V161411, V162034) 

Did_You_register <- anes16 %>% select(V161011)

Did_You_Vote <- anes16 %>% select(V162034)

TV_Cleaned <- read.csv("C:/Users/Owner/Downloads/TV Cleaned - Sheet1.csv")

```


### Data Grouped

```{r}

Traditional_Political_News_Programs <- TV %>% select(V161364, V161367, V161380, V161384, V161388, V161390, V161396, V161399, V161405)

Entertainment_or_Opinion_Political_News_Programs <- TV %>% select(V161365, V161370, V161371, V161372, V161375, V161379, V161381, V161382, V161386,V161391, V161393, V161400, V161403, V161404, V161409)

Entertainment_Programs_that_are_Expressly_Political <- TV %>% select(V161385, V161389, V161402, V161406,V161411)

Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue <- TV %>% select(V161366, V161368, V161374, V161377, V161387, V161392, V161397, V161401)

Entertainment_Programs_with_little_to_No_Political_Content <- TV %>% select(V161369, V161373, V161376, V161378, V161383, V161394, V161395, V161398, V161407, V161410)

Twenty_Twenty <- TV %>% select (V161364) %>% unlist()
All_In_with_Chris_Hayes	<- TV %>% select (V161365) %>% unlist()
The_Blacklist <- TV %>% select (V161366) %>% unlist()
CBS_Evening_News_with_Scott_Pelley <- TV %>% select (V161367) %>% unlist()
Criminal_Minds <- TV %>% select (V161368) %>% unlist()
Empire <- TV %>% select (V161369) %>% unlist()
Hannity	<- TV %>% select (V161370) %>% unlist()
Jimmy_Kimmel_Live <- TV %>% select (V161371) %>% unlist()
The_Kelly_File <- TV %>% select (V161372) %>% unlist()
Modern_Family <- TV %>% select (V161373) %>% unlist()
NCIS <-	 TV %>% select (V161374) %>% unlist()
The_Nightly_Show_with_Larry_Wilmore	<- TV %>% select (V161375) %>% unlist()
Sunday_Night_Football <-  TV %>% select (V161376) %>% unlist()
Scorpion <-  TV %>% select (V161377) %>% unlist()
The_Simpsons <-  TV %>% select (V161378) %>% unlist()
Today <- TV %>% select (V161379) %>% unlist()
Sixty_Minutes <- TV %>% select (V161380) %>% unlist()
Anderson_Cooper_Three_Hundred_and_Sixty <- TV %>% select (V161381) %>% unlist()
CBS_This_Morning <- TV %>% select (V161382) %>% unlist()
Dancing_with_the_Stars <-  TV %>% select (V161383) %>% unlist()
Face_the_Nation <- TV %>% select (V161384) %>% unlist()
House_of_Cards <- TV %>% select (V161385) %>% unlist()
Hardball_with_Chris_Matthews <- TV %>% select (V161386) %>% unlist()
Judge_Judy <- TV %>% select (V161387) %>% unlist()
Meet_the_Press	<- TV %>% select (V161388) %>% unlist()
Game_of_Thrones	<- TV %>% select (V161389) %>% unlist()
NBC_Nightly_News_with_Lester_Holt <- TV %>% select (V161390) %>% unlist()
On_the_Record_with_Greta_Van_Susteren <- TV %>% select (V161391) %>% unlist()
Daredevil <- TV %>% select (V161392) %>% unlist()
The_Rachel_Maddow_Show <- TV %>% select (V161393) %>% unlist()
Shark_Tank <- TV %>% select (V161394) %>% unlist()
The_Voice <- TV %>% select(V161395) %>% unlist()
ABC_World_News_with_David_Muir <- TV %>% select (V161396) %>% unlist()
Blue_bloods <-  TV %>% select (V161397) %>% unlist()
Conan <-  TV %>% select (V161398) %>% unlist()
Dateline_NBC <-	TV %>% select (V161399) %>% unlist()
Good_Morning_America <- TV %>% select (V161400) %>% unlist()
Hawaii_Five_O <- TV %>% select (V161401) %>% unlist()
Madam_Secretary	<- TV %>% select (V161402) %>% unlist()
Nancy_Grace	<- TV %>% select (V161403) %>% unlist()
Erin_Burnett_OutFront <- TV %>% select (V161404) %>% unlist()
PBS_News_Hour <-  TV %>% select (V161405) %>% unlist()
Scandal <- TV %>% select (V161406) %>% unlist()
The_Big_Bang_Theory <- TV %>% select (V161407) %>% unlist()
The_Late_Show_with_Stephen_Colbert <- TV %>% select(V161408) %>% unlist()
The_O_Reilly_Factor	<-	 TV %>% select (V161409) %>% unlist()
The_Tonight_Show_Starring_Jimmy_Fallon <- TV %>% select(V161410) %>% unlist()
Alpha_House	<- TV %>% select(V161411) %>% unlist()



```

### Regression for Traditional Political News Programs and Registration Status ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))

Traditional_Political_News_Programs_Moded_register <- as.data.frame(Twenty_Twenty + CBS_Evening_News_with_Scott_Pelley + Sixty_Minutes + Face_the_Nation + Meet_the_Press + NBC_Nightly_News_with_Lester_Holt + ABC_World_News_with_David_Muir + Dateline_NBC + PBS_News_Hour) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Traditional_Political_News_Programs_Moded_register_lm <- lm(register ~  Twenty_Twenty + CBS_Evening_News_with_Scott_Pelley + Sixty_Minutes + Face_the_Nation + Meet_the_Press + NBC_Nightly_News_with_Lester_Holt + ABC_World_News_with_David_Muir + Dateline_NBC + PBS_News_Hour , data = anes_clean)

summary(Traditional_Political_News_Programs_Moded_register_lm)

coefplot::coefplot(Traditional_Political_News_Programs_Moded_register_lm)


```
### Regression for Entertainment or Opinion Political News Programs and Registration Status ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))

Entertainment_or_Opinion_Political_News_Programs_Moded_register <- as.data.frame(All_In_with_Chris_Hayes + Hannity + Jimmy_Kimmel_Live + The_Kelly_File + The_Nightly_Show_with_Larry_Wilmore + Today + Anderson_Cooper_Three_Hundred_and_Sixty + CBS_This_Morning + Hardball_with_Chris_Matthews + On_the_Record_with_Greta_Van_Susteren + The_Rachel_Maddow_Show + Good_Morning_America + Nancy_Grace + Erin_Burnett_OutFront + The_O_Reilly_Factor) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_or_Opinion_Political_News_Programs_Moded_register_lm <- lm(register ~ All_In_with_Chris_Hayes + Hannity + Jimmy_Kimmel_Live + The_Kelly_File + The_Nightly_Show_with_Larry_Wilmore + Today + Anderson_Cooper_Three_Hundred_and_Sixty + CBS_This_Morning + Hardball_with_Chris_Matthews + On_the_Record_with_Greta_Van_Susteren + The_Rachel_Maddow_Show + Good_Morning_America + Nancy_Grace + Erin_Burnett_OutFront + The_O_Reilly_Factor , data = anes_clean)

summary(Entertainment_or_Opinion_Political_News_Programs_Moded_register_lm)

coefplot::coefplot(Entertainment_or_Opinion_Political_News_Programs_Moded_register_lm)

```
### Regression for Entertainment Programs that are Expressly Political and Registration Staus ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))

Entertainment_Programs_that_are_Expressly_Political_Moded_register <- as.data.frame(House_of_Cards + Game_of_Thrones + Madam_Secretary + Scandal + Alpha_House) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_Programs_that_are_Expressly_Political_Moded_register_lm <- lm(register ~  House_of_Cards + Game_of_Thrones + Madam_Secretary + Scandal + Alpha_House , data = anes_clean)

summary(Entertainment_Programs_that_are_Expressly_Political_Moded_register_lm)

coefplot::coefplot(Entertainment_Programs_that_are_Expressly_Political_Moded_register_lm)

```
### Regresion for Entertainment Programs that are not Expressly Political but Focus on a salient Political issue and Registration Status ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))

Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_register <- as.data.frame( The_Blacklist + Criminal_Minds + NCIS + Scorpion + Judge_Judy + Daredevil + Blue_bloods + Hawaii_Five_O) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_register_lm <- lm(register ~ The_Blacklist + Criminal_Minds + NCIS + Scorpion + Judge_Judy + Daredevil + Blue_bloods + Hawaii_Five_O, data = anes_clean)

summary(Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_register_lm)

coefplot::coefplot(Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_register_lm)

```

### Regresion for Entertainment Programs with little to No Political Content and Registration Status ###

```{r}
clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))

Entertainment_Programs_with_little_to_No_Political_Content_moded_register <- as.data.frame(Empire + Modern_Family + Sunday_Night_Football + The_Simpsons + Dancing_with_the_Stars + Shark_Tank + The_Voice + Conan + The_Big_Bang_Theory + The_Tonight_Show_Starring_Jimmy_Fallon) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_Programs_with_little_to_No_Political_Content_moded_register_lm <- lm(register ~ Empire + Modern_Family + Sunday_Night_Football + The_Simpsons + Dancing_with_the_Stars + Shark_Tank + The_Voice + Conan + The_Big_Bang_Theory + The_Tonight_Show_Starring_Jimmy_Fallon, data = anes_clean)

summary(Entertainment_Programs_with_little_to_No_Political_Content_moded_register_lm)

coefplot::coefplot(Entertainment_Programs_with_little_to_No_Political_Content_moded_register_lm)






```

### Regression for All Variables and Registration Status ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))


All_Variables_Moded_register <- as.data.frame(Twenty_Twenty + CBS_Evening_News_with_Scott_Pelley + Sixty_Minutes + Face_the_Nation + Meet_the_Press + NBC_Nightly_News_with_Lester_Holt + ABC_World_News_with_David_Muir + Dateline_NBC + PBS_News_Hour + All_In_with_Chris_Hayes + Hannity + Jimmy_Kimmel_Live + The_Kelly_File + The_Nightly_Show_with_Larry_Wilmore + Today + Anderson_Cooper_Three_Hundred_and_Sixty + CBS_This_Morning + Hardball_with_Chris_Matthews + On_the_Record_with_Greta_Van_Susteren + The_Rachel_Maddow_Show + Good_Morning_America + Nancy_Grace + Erin_Burnett_OutFront + The_O_Reilly_Factor + House_of_Cards + Game_of_Thrones + Madam_Secretary + Scandal + Alpha_House + The_Blacklist + Criminal_Minds + NCIS + Scorpion + Judge_Judy + Daredevil + Blue_bloods + Hawaii_Five_O + Empire + Modern_Family + Sunday_Night_Football +  The_Simpsons + Dancing_with_the_Stars + Shark_Tank + The_Voice + Conan + The_Big_Bang_Theory + The_Tonight_Show_Starring_Jimmy_Fallon) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

All_Variables_Moded_register_lm <- lm(register ~ Twenty_Twenty + CBS_Evening_News_with_Scott_Pelley + Sixty_Minutes + Face_the_Nation + Meet_the_Press + NBC_Nightly_News_with_Lester_Holt + ABC_World_News_with_David_Muir + Dateline_NBC + PBS_News_Hour + All_In_with_Chris_Hayes + Hannity + Jimmy_Kimmel_Live + The_Kelly_File + The_Nightly_Show_with_Larry_Wilmore + Today + Anderson_Cooper_Three_Hundred_and_Sixty + CBS_This_Morning + Hardball_with_Chris_Matthews + On_the_Record_with_Greta_Van_Susteren + The_Rachel_Maddow_Show + Good_Morning_America + Nancy_Grace + Erin_Burnett_OutFront + The_O_Reilly_Factor + House_of_Cards + Game_of_Thrones + Madam_Secretary + Scandal + Alpha_House + The_Blacklist + Criminal_Minds + NCIS + Scorpion + Judge_Judy + Daredevil + Blue_bloods + Hawaii_Five_O + Empire + Modern_Family + Sunday_Night_Football +  The_Simpsons + Dancing_with_the_Stars + Shark_Tank + The_Voice + Conan + The_Big_Bang_Theory + The_Tonight_Show_Starring_Jimmy_Fallon, data = anes_clean)

summary(All_Variables_Moded_register_lm)

coefplot::coefplot (All_Variables_Moded_register_lm)

```

### Regression for Traditional Political News Programs and Turnout Grouped ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(vote = case_when(
V162034 == 2 ~ 0,
V162034 == 1 ~ 1))


Traditional_Political_News_Programs_Moded_vote_grouped <- as.data.frame(Twenty_Twenty + CBS_Evening_News_with_Scott_Pelley + Sixty_Minutes + Face_the_Nation + Meet_the_Press + NBC_Nightly_News_with_Lester_Holt + ABC_World_News_with_David_Muir + Dateline_NBC + PBS_News_Hour) %>%
    rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()



Traditional_Political_News_Programs_Moded_vote_grouped_lm <- lm(vote ~  Traditional_Political_News_Programs_Moded_vote_grouped , data = anes_clean)

summary(Traditional_Political_News_Programs_Moded_vote_grouped_lm)

coefplot::coefplot(Traditional_Political_News_Programs_Moded_vote_grouped_lm)


```

### Regression for Entertainment or Opinion Political News Programs and Turnout Grouped  ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(vote = case_when(
V162034 == 2 ~ 0,
V162034 == 1 ~ 1))

Entertainment_or_Opinion_Political_News_Programs_Moded_vote_grouped <- as.data.frame(All_In_with_Chris_Hayes + Hannity + Jimmy_Kimmel_Live + The_Kelly_File + The_Nightly_Show_with_Larry_Wilmore + Today + Anderson_Cooper_Three_Hundred_and_Sixty + CBS_This_Morning + Hardball_with_Chris_Matthews + On_the_Record_with_Greta_Van_Susteren + The_Rachel_Maddow_Show + Good_Morning_America + Nancy_Grace + Erin_Burnett_OutFront + The_O_Reilly_Factor) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_or_Opinion_Political_News_Programs_Moded_vote_grouped_lm <- lm(vote ~Entertainment_or_Opinion_Political_News_Programs_Moded_vote_grouped , data = anes_clean)

summary(Entertainment_or_Opinion_Political_News_Programs_Moded_vote_grouped_lm)

coefplot::coefplot(Entertainment_or_Opinion_Political_News_Programs_Moded_vote_grouped_lm)

```

 ### Regression for Entertainment Programs that are Expressly Political and Turnout Grouped ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(vote = case_when(
V162034 == 2 ~ 0,
V162034 == 1 ~ 1))

Entertainment_Programs_that_are_Expressly_Political_Moded_vote_grouped <- as.data.frame (House_of_Cards + Game_of_Thrones + Madam_Secretary + Scandal + Alpha_House) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_Programs_that_are_Expressly_Political_Moded_vote_grouped_lm <- lm (vote ~ Entertainment_Programs_that_are_Expressly_Political_Moded_vote_grouped , data = anes_clean)

summary(Entertainment_Programs_that_are_Expressly_Political_Moded_vote_grouped_lm)

coefplot::coefplot(Entertainment_Programs_that_are_Expressly_Political_Moded_vote_grouped_lm)

```

### Regresion for Entertainment Programs that are not Expressly Political but Focus on a Salient Political issue and Turnout Grouped ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(vote = case_when(
V162034 == 2 ~ 0,
V162034 == 1 ~ 1))

Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_vote_grouped <- as.data.frame(The_Blacklist + Criminal_Minds + NCIS + Scorpion + Judge_Judy + Daredevil + Blue_bloods + Hawaii_Five_O) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_vote_grouped_lm <- lm(vote ~ Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_vote_grouped, data = anes_clean)

summary(Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_vote_grouped_lm)

coefplot::coefplot(Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_vote_grouped_lm)

```

### Regresion for Entertainment Programs with little to No Political Content and Turnout Grouped ###

```{r}
clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(vote = case_when(
V162034 == 2 ~ 0,
V162034 == 1 ~ 1))

Entertainment_Programs_with_little_to_No_Political_Content_moded_vote_grouped <- as.data.frame(Empire + Modern_Family + Sunday_Night_Football + The_Simpsons + Dancing_with_the_Stars + Shark_Tank + The_Voice + Conan + The_Big_Bang_Theory + The_Tonight_Show_Starring_Jimmy_Fallon) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_Programs_with_little_to_No_Political_Content_moded_vote_grouped_lm <- lm(vote ~ Entertainment_Programs_with_little_to_No_Political_Content_moded_vote_grouped , data = anes_clean)

summary(Entertainment_Programs_with_little_to_No_Political_Content_moded_vote_grouped_lm)

coefplot::coefplot(Entertainment_Programs_with_little_to_No_Political_Content_moded_vote_grouped_lm)

```

### Regression for All Variables and Turnout Grouped ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(vote = case_when(
V162034 == 2 ~ 0,
V162034 == 1 ~ 1))


All_Variables_Moded_vote_grouped <- as.data.frame(Twenty_Twenty + CBS_Evening_News_with_Scott_Pelley + Sixty_Minutes + Face_the_Nation + Meet_the_Press + NBC_Nightly_News_with_Lester_Holt + ABC_World_News_with_David_Muir + Dateline_NBC + PBS_News_Hour + All_In_with_Chris_Hayes + Hannity + Jimmy_Kimmel_Live + The_Kelly_File + The_Nightly_Show_with_Larry_Wilmore + Today + Anderson_Cooper_Three_Hundred_and_Sixty + CBS_This_Morning + Hardball_with_Chris_Matthews + On_the_Record_with_Greta_Van_Susteren + The_Rachel_Maddow_Show + Good_Morning_America + Nancy_Grace + Erin_Burnett_OutFront + The_O_Reilly_Factor + House_of_Cards + Game_of_Thrones + Madam_Secretary + Scandal + Alpha_House + The_Blacklist + Criminal_Minds + NCIS + Scorpion + Judge_Judy + Daredevil + Blue_bloods + Hawaii_Five_O + Empire + Modern_Family + Sunday_Night_Football +  The_Simpsons + Dancing_with_the_Stars + Shark_Tank + The_Voice + Conan + The_Big_Bang_Theory + The_Tonight_Show_Starring_Jimmy_Fallon) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

All_Variables_Moded_vote_grouped_lm <- lm(vote ~ All_Variables_Moded_vote_grouped ,  data = anes_clean)

summary(All_Variables_Moded_vote_grouped_lm)

coefplot::coefplot (All_Variables_Moded_vote_grouped_lm)
```

### Regression for All Grouped Variables Grouped and Turnout ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(vote = case_when(
V162034 == 2 ~ 0,
V162034 == 1 ~ 1))

All_Variables_Moded_vote_grouped_grouped <- as.data.frame(
Traditional_Political_News_Programs_Moded_vote_grouped + 
Entertainment_or_Opinion_Political_News_Programs_Moded_vote_grouped +
Entertainment_Programs_that_are_Expressly_Political_Moded_vote_grouped + 
Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_vote_grouped +
Entertainment_Programs_with_little_to_No_Political_Content_moded_vote_grouped 
)%>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()


All_Variables_Moded_vote_grouped_grouped_lm <- lm(vote ~ All_Variables_Moded_vote_grouped_grouped , data = anes_clean)

summary (All_Variables_Moded_vote_grouped_grouped_lm)

coefplot::coefplot (All_Variables_Moded_vote_grouped_grouped_lm)

```


### Regression for Traditional Political News Programs and Registration Status Grouped ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))

Traditional_Political_News_Programs_Moded_register_grouped <- as.data.frame(Twenty_Twenty + CBS_Evening_News_with_Scott_Pelley + Sixty_Minutes + Face_the_Nation + Meet_the_Press + NBC_Nightly_News_with_Lester_Holt + ABC_World_News_with_David_Muir + Dateline_NBC + PBS_News_Hour) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Traditional_Political_News_Programs_Moded_register_grouped_lm <- lm(register ~ Traditional_Political_News_Programs_Moded_register_grouped, data = anes_clean)

summary(Traditional_Political_News_Programs_Moded_register_grouped_lm)

coefplot::coefplot(Traditional_Political_News_Programs_Moded_register_grouped_lm)


```
### Regression for Entertainment or Opinion Political News Programs and Registration Status Grouped ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))

Entertainment_or_Opinion_Political_News_Programs_Moded_register_grouped <- as.data.frame (All_In_with_Chris_Hayes + Hannity + Jimmy_Kimmel_Live + The_Kelly_File + The_Nightly_Show_with_Larry_Wilmore + Today + Anderson_Cooper_Three_Hundred_and_Sixty + CBS_This_Morning + Hardball_with_Chris_Matthews + On_the_Record_with_Greta_Van_Susteren + The_Rachel_Maddow_Show + Good_Morning_America + Nancy_Grace + Erin_Burnett_OutFront + The_O_Reilly_Factor) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_or_Opinion_Political_News_Programs_Moded_register_grouped_lm <- lm (register ~ Entertainment_or_Opinion_Political_News_Programs_Moded_register_grouped , data = anes_clean)

summary(Entertainment_or_Opinion_Political_News_Programs_Moded_register_grouped_lm)

coefplot::coefplot(Entertainment_or_Opinion_Political_News_Programs_Moded_register_grouped_lm)

```
### Regression for Entertainment Programs that are Expressly Political and Registration Staus Grouped ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))

Entertainment_Programs_that_are_Expressly_Political_Moded_register_grouped <- as.data.frame(House_of_Cards + Game_of_Thrones + Madam_Secretary + Scandal + Alpha_House) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_Programs_that_are_Expressly_Political_Moded_register_grouped_lm <- lm(register ~ Entertainment_Programs_that_are_Expressly_Political_Moded_register_grouped , data = anes_clean)

summary(Entertainment_Programs_that_are_Expressly_Political_Moded_register_grouped_lm)

coefplot::coefplot(Entertainment_Programs_that_are_Expressly_Political_Moded_register_grouped_lm)

```
### Regresion for Entertainment Programs that are not Expressly Political but Focus on a salient Political issue and Registration Status Grouped ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))

Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_register_grouped <- as.data.frame( The_Blacklist + Criminal_Minds + NCIS + Scorpion + Judge_Judy + Daredevil + Blue_bloods + Hawaii_Five_O) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_register_grouped_lm <- lm(register ~ Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_register_grouped , data = anes_clean)

summary(Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_register_grouped_lm)

coefplot::coefplot(Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_register_grouped_lm)

```

### Regresion for Entertainment Programs with little to No Political Content and Registration Status Grouped ###

```{r}
clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))

Entertainment_Programs_with_little_to_No_Political_Content_moded_register_grouped <- as.data.frame(Empire + Modern_Family + Sunday_Night_Football + The_Simpsons + Dancing_with_the_Stars + Shark_Tank + The_Voice + Conan + The_Big_Bang_Theory + The_Tonight_Show_Starring_Jimmy_Fallon) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

Entertainment_Programs_with_little_to_No_Political_Content_moded_register_grouped_lm <- lm(register ~ Entertainment_Programs_with_little_to_No_Political_Content_moded_register_grouped , anes_clean)

summary(Entertainment_Programs_with_little_to_No_Political_Content_moded_register_grouped_lm)

coefplot::coefplot(Entertainment_Programs_with_little_to_No_Political_Content_moded_register_grouped_lm)

```

### Regression for All Variables and Registration Status Grouped ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))


All_Variables_Moded_register_grouped <- as.data.frame(Twenty_Twenty + CBS_Evening_News_with_Scott_Pelley + Sixty_Minutes + Face_the_Nation + Meet_the_Press + NBC_Nightly_News_with_Lester_Holt + ABC_World_News_with_David_Muir + Dateline_NBC + PBS_News_Hour + All_In_with_Chris_Hayes + Hannity + Jimmy_Kimmel_Live + The_Kelly_File + The_Nightly_Show_with_Larry_Wilmore + Today + Anderson_Cooper_Three_Hundred_and_Sixty + CBS_This_Morning + Hardball_with_Chris_Matthews + On_the_Record_with_Greta_Van_Susteren + The_Rachel_Maddow_Show + Good_Morning_America + Nancy_Grace + Erin_Burnett_OutFront + The_O_Reilly_Factor + House_of_Cards + Game_of_Thrones + Madam_Secretary + Scandal + Alpha_House + The_Blacklist + Criminal_Minds + NCIS + Scorpion + Judge_Judy + Daredevil + Blue_bloods + Hawaii_Five_O + Empire + Modern_Family + Sunday_Night_Football +  The_Simpsons + Dancing_with_the_Stars + Shark_Tank + The_Voice + Conan + The_Big_Bang_Theory + The_Tonight_Show_Starring_Jimmy_Fallon) %>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

All_Variables_Moded_register_grouped_lm <- lm(register ~ All_Variables_Moded_register_grouped , data = anes_clean)

summary(All_Variables_Moded_register_grouped_lm)

coefplot::coefplot (All_Variables_Moded_register_grouped_lm)
```

### Regression for All Variables Grouped Grouped Registration Status  ###

```{r}

clean <- function(x){ifelse (x < 0, NA, x)}
anes_clean <- anes16 %>%
    mutate(across (everything(), clean)) %>%

mutate(register = case_when(
V161011 == 2 ~ 0,
V161011 == 1 ~ 1))

All_Variables_Moded_register_grouped_grouped <- as.data.frame (Traditional_Political_News_Programs_Moded_register_grouped +
Entertainment_or_Opinion_Political_News_Programs_Moded_register_grouped +
Entertainment_Programs_that_are_Expressly_Political_Moded_register_grouped +
Entertainment_Programs_that_are_not_Expressly_Political_but_Focus_on_a_salient_Political_issue_Moded_register_grouped +
Entertainment_Programs_with_little_to_No_Political_Content_moded_register_grouped)%>%
rename(count = 1) %>%
    mutate(count = ifelse(count <0, NA, count)) %>% unlist()

All_Variables_Moded_register_grouped_grouped_lm <- lm(register ~ All_Variables_Moded_register_grouped_grouped , data = anes_clean)

summary(All_Variables_Moded_register_grouped_grouped_lm)

coefplot::coefplot (All_Variables_Moded_register_grouped_grouped_lm)

```

Just like with my last post my prediction was dead wrong. In fact these shows had a very different affect on registration that they did on turnout. Way more shows individually had a significant (at the 5% level) affect on registration than turnout, and furthermore each group of shows had a significant effect on registration. This is very different than with turnout where none of the groups together or alone had an affect on turnout. Even without controlling for other variables it seems that these shows have an impact on whether watchers are registered to vote. It is not clear why that is the case or why they have such a stronger affect on registration than on turnout. This could have interesting implications for campaigns it could perhaps mean that campaigns should use TV ad buys to focus on registering watchers rather than turnout if advertising is a factor in the affect these shows had on registration it could be that is the shows themselves and political advertising has no impact on the effect these shows have on registration. I think that my future project that will look at the affect on turnout per dollar per person could also apply here excpet it would be affect on registration per dollar per person. I would also like to do a project where I look at the effect that streamed shows without have on turnout and registration versus the effect that shows without ads have on turnout and registration to see whether advertising is a factor at all in the affect these shows (or others) have on turnout and registration. Again this is a work in progress we still need to control for other factors, clean up the code and graphs, and this was done with an unsophisticated linear regression model by sudents without strong backgrounds in statistics. 

